fdcoexist

### 2018-09-04 meta_simulations.Rmd
Additional Rmd for meta simulations

@@

This document presents the relationships between functional traits of species and an environmental gradient.

Our coexistence model is developed following this equation:

\begin{equation}
N_{t+1, i, x} = \frac{R_{i, x} \times N_{t, i, x}}{1 + A \times \alpha_i}
\end{equation}

with

\begin{gather}
\alpha_i = \sum_{j = 1, j \neq i}^{S} N_{t, j, x} \times (1 - \delta_{ij})\\
R_{i, x} = k \times \exp\left(- \frac{(\text{trait}_i - \text{env}_x)^2}{2\times \text{width}^2}\right)
\end{gather}

If we replace $\alpha_i$ and $R_{i, x}$ in the first equation it gives:

\begin{equation}
N_{t+1, i, x} = \frac{
k \times \exp\left(- \displaystyle\frac{(\text{trait}_i - \text{env}_x)^2}{2\times \text{width}^2}\right) \times N_{t, i, x}}{
1 + A \times \displaystyle\sum_{j = 1, j \neq i}^{S} N_{t, j, x} \times (1 - \delta_{ij})
}
\end{equation}

The equation above only considers inter-specific competition when $j \neq i$ in the sum. We can however add intra-specific competition when $j = i$. Each site has a species-specific carrying capacity $K$ as the number of individuals approaches this carrying capacity the intra-specific competition increases:
\begin{equation}
\alpha_{ii} = B \times N_{t,i,x}
\end{equation}

Thus the equation becomes:

\begin{equation}
N_{t+1, i, x} = \frac{
k \times \exp\left(- \displaystyle\frac{(\text{trait}_i - \text{env}_x)^2}{2\times \text{width}^2}\right) \times N_{t, i, x}}{
1 + A \times \displaystyle\sum_{j = 1,~j \neq i}^{S} N_{t, j, x}  (1 - \delta_{ij}) +
B \times N_{t,i,x}
}
\end{equation}

with $A$ the coefficient scaling inter-specific competition and $B$ the one for intra-specific competition.

Because several traits participate to the growth term depending on their contribution we can rewrite the growth term as:
\begin{equation}
R_{i, x} = \sum_{g = 1}^T w_g \times k \times \exp\left(- \frac{(\text{trait}_{g,i} - \text{env}_x)^2}{2\times \text{width}^2}\right)
\end{equation}

with $g$ the trait number, $0 \leq w_g \leq 1$ the contribution of this trait to growth (and $\sum_{g = 1}^T w_g = 1$), $\text{trait}_{g, i}$ the trait number $g$ of species $i$.

# Constant environmental filtering strength

## Without Competition (only intra-specific competition)

We can run the simulations without any competition `A = 0` to see if we see the theoretical patterns.

### No correlations among traits

```{r simul_no_compet_no_corr}
no_compet_no_cor <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = uncor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = 0, B = B, d = d,
                 k = k, width = env_width)
    })

# Takes simulation results and put them as an exploitable data.frame with only
# gen = 150 abundances
no_compet_no_cor_df = tidy_simulation_list(no_compet_no_cor,
                                           set_of_traits = uncor_traits,
                                           trait_scenarios = trait_scenarios)

no_compet_no_cor_label = paste0("Only intra comp.; ",
                                d * 100, "% dispersal;",
                                " 3 uncorrelated traits")
```

```{r no_compet_no_cor_abund_env, eval = FALSE}
plot_no_compet_no_cor_abund_env = fig_abund_env(no_compet_no_cor_df,
                                                no_compet_no_cor_label)

plot_no_compet_no_cor_abund_env
```

```{r no_compet_no_cor_cwm_env, eval = FALSE}
plot_no_compet_no_cor_cwm_env = fig_cwm_env(no_compet_no_cor_df,
                                            no_compet_no_cor_label)
plot_no_compet_no_cor_cwm_env
```

```{r no_compet_no_cor_cwm_env_abund, eval = FALSE}
plot_no_compet_no_cor_cwm_env_abund = fig_cwm_env_abund(no_compet_no_cor_df,
                                                        no_compet_no_cor_label,
                                                        given_trans = "log10")

plot_no_compet_no_cor_cwm_env_abund
```

```{r no_compet_no_cor_df_ind_landscape}
plot_no_compet_no_cor_df_ind_landscape = fig_ind_landscape(no_compet_no_cor_df,
                                                           no_compet_no_cor_label,
                                                           n_bins = 22,
                                                           given_trans = "identity")

plot_no_compet_no_cor_df_ind_landscape
```

### Low correlations among traits

```{r simul_no_compet_low_cor}
no_compet_low_cor <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = low_cor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = 0, B = B, d = d,
                 k = k, width = env_width)
    })

# Takes simulation results and put them as an exploitable data.frame with only
# gen = 150 abundances
no_compet_low_cor_df = tidy_simulation_list(no_compet_low_cor,
                                            low_cor_traits,
                                            trait_scenarios)

no_compet_low_cor_label = paste0("Only intra comp.; ",
                                 d * 100, "% dispersal;",
                                 " 3 low correlated (r = 0.3) traits")
```

```{r no_compet_low_cor_df_ind_landscape}
plot_no_compet_low_cor_df_ind_landscape = fig_ind_landscape(no_compet_low_cor_df,
                                                            no_compet_low_cor_label,
                                                            n_bins = 17,
                                                            given_trans = "identity")

plot_no_compet_low_cor_df_ind_landscape
```

### High correlations among traits

```{r simul_no_compet_high_cor}
no_compet_high_cor <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = high_cor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = 0, B = B, d = d,
                 k = k, width = env_width)
    })

# Takes simulation results and put them as an exploitable data.frame with only
# gen = 150 abundances
no_compet_high_cor_df = tidy_simulation_list(no_compet_high_cor,
                                             high_cor_traits,
                                             trait_scenarios)

no_compet_high_cor_label = paste0("Only intra comp.; ",
                                  d * 100, "% dispersal;",
                                  " 3 high correlated (r = 0.7) traits")
```

```{r no_compet_high_cor_df_ind_landscape}
plot_no_compet_high_cor_df_ind_landscape = fig_ind_landscape(no_compet_high_cor_df,
                                                             no_compet_high_cor_label,
                                                             n_bins = 17)

plot_no_compet_high_cor_df_ind_landscape
```

## With competition

### No correlations among traits

```{r simul_compet_no_corr}
compet_no_cor <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = uncor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = A, B = B, d = d,
                 k = k, width = env_width)
    })

# Takes simulation results and put them as an exploitable data.frame with only
# gen = 150 abundances
compet_no_cor_df = tidy_simulation_list(compet_no_cor,
                                        set_of_traits = uncor_traits,
                                        trait_scenarios = trait_scenarios)

compet_no_cor_label = paste0("Competition (A = ", A, "); ",
                             d * 100, "% dispersal;",
                             " 3 uncorrelated traits")
```

```{r compet_no_cor_df_ind_landscape}
plot_compet_no_cor_df_ind_landscape = fig_ind_landscape(compet_no_cor_df,
                                                        compet_no_cor_label,
                                                        n_bins = 22)

plot_compet_no_cor_df_ind_landscape
```

### Low correlations among traits

```{r simul_compet_low_corr}
compet_low_cor <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = uncor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = A, B = B, d = d,
                 k = k, width = env_width)
    })

# Takes simulation results and put them as an exploitable data.frame with only
# gen = 150 abundances
compet_low_cor_df = tidy_simulation_list(compet_low_cor,
                                         set_of_traits = low_cor_traits,
                                         trait_scenarios = trait_scenarios)

compet_low_cor_label = paste0("Competition (A = ", A, "); ",
                              d * 100, "% dispersal;",
                              " 3 correlated traits (r = 0.3)")
```

```{r compet_low_cor_df_ind_landscape}
plot_compet_low_cor_df_ind_landscape = fig_ind_landscape(compet_low_cor_df,
                                                         compet_low_cor_label,
                                                         n_bins = 17)

plot_compet_low_cor_df_ind_landscape
```

### High correlations among traits

```{r simul_compet_high_corr}
compet_high_cor <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = uncor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = A, B = B, d = d,
                 k = k, width = env_width)
    })

# Takes simulation results and put them as an exploitable data.frame with only
# gen = 150 abundances
compet_high_cor_df = tidy_simulation_list(compet_high_cor,
                                          set_of_traits = high_cor_traits,
                                          trait_scenarios = trait_scenarios)

compet_high_cor_label = paste0("Competition (A = ", A, "); ",
                               d * 100, "% dispersal;",
                               " 3 correlated traits (r = 0.7)")
```

```{r compet_high_cor_df_ind_landscape}
plot_compet_high_cor_df_ind_landscape = fig_ind_landscape(compet_high_cor_df,
                                                          compet_high_cor_label,
                                                          n_bins = 17)
plot_compet_high_cor_df_ind_landscape
```

# With varying environmental filtering strength

## Without Competition (only intra-specific competition)

In this section, the environmental filtering selects for a narrower trait range
towards the end of the environmental gradient.

### No correlations among traits

```{r simul_no_compet_no_corr var_strength}

no_compet_no_cor_var <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = uncor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = 0, B = B, d = d,
                 k = k, width = var_width)
    })

# Takes simulation results and put them as an exploitable data.frame with only
# gen = 150 abundances
no_compet_no_cor_var_df = tidy_simulation_list(no_compet_no_cor_var,
                                               set_of_traits = uncor_traits,
                                               trait_scenarios = trait_scenarios)

no_compet_no_cor_var_label = paste0("Only intra compet; ",
                                    d * 100, "% dispersal;",
                                    " 3 uncorrelated traits")
```

```{r no_compet_no_cor_df_ind_landscape var_strength}
plot_no_compet_no_cor_df_ind_var_landscape = fig_ind_landscape(no_compet_no_cor_var_df,
                                                               no_compet_no_cor_var_label,
                                                               n_bins = 22,
                                                               given_trans = "identity")

plot_no_compet_no_cor_df_ind_var_landscape
```

### Low correlations among traits

```{r simul_no_compet_low_cor var_strength}
no_compet_low_cor_var <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = low_cor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = 0, B = B, d = d,
                 k = k, width = var_width)
    })

# Takes simulation results and put them as an exploitable data.frame with only
# gen = 150 abundances
no_compet_low_cor_var_df = tidy_simulation_list(no_compet_low_cor_var,
                                                low_cor_traits,
                                                trait_scenarios)

no_compet_low_cor_var_label = paste0("Only intra compet; ",
                                     d * 100, "% dispersal;",
                                     " 3 low correlated (r = 0.3) traits")
```

```{r no_compet_low_cor_df_ind_landscape var_strength}
plot_no_compet_low_cor_df_ind_var_landscape = fig_ind_landscape(no_compet_low_cor_var_df,
                                                                no_compet_low_cor_var_label,
                                                                n_bins = 17,
                                                                given_trans = "identity")

plot_no_compet_low_cor_df_ind_var_landscape
```

### High correlations among traits

```{r simul_no_compet_high_cor var_strength}
no_compet_high_cor_var <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = high_cor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = 0, B = B, d = d,
                 k = k, width = var_width)
    })

# Takes simulation results and put them as an exploitable data.frame with only
# gen = 150 abundances
no_compet_high_cor_var_df = tidy_simulation_list(no_compet_high_cor_var,
                                                 high_cor_traits,
                                                 trait_scenarios)

no_compet_high_cor_var_label = paste0("Only intra compet; ",
                                      d * 100, "% dispersal;",
                                      " 3 high correlated (r = 0.7) traits")
```

```{r no_compet_high_cor_df_ind_landscape var_strength}
plot_no_compet_high_cor_df_ind_var_landscape = fig_ind_landscape(no_compet_high_cor_var_df,
                                                                 no_compet_high_cor_var_label,
                                                                 n_bins = 17)

plot_no_compet_high_cor_df_ind_var_landscape
```

## With competition

### No correlations among traits

```{r simul_compet_no_corr var_strength}
compet_no_cor_var <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = uncor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = A, B=B, d = d,
                 k = k, width = var_width)
    })

# Takes simulation results and put them as an exploitable data.frame with only
# gen = 150 abundances
compet_no_cor_var_df = tidy_simulation_list(compet_no_cor_var,
                                            set_of_traits = uncor_traits,
                                            trait_scenarios = trait_scenarios)

compet_no_cor_var_label = paste0("Competition (A = ", A, "); ",
                                 d * 100, "% dispersal;",
                                 " 3 uncorrelated traits")
```

```{r compet_no_cor_df_ind_landscape var_strength}
plot_compet_no_cor_df_ind_var_landscape = fig_ind_landscape(compet_no_cor_var_df,
                                                            compet_no_cor_var_label,
                                                            n_bins = 22)

plot_compet_no_cor_df_ind_var_landscape
```

### Low correlations among traits

```{r simul_compet_low_corr var_strength}
compet_low_cor_var <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = uncor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = A, B=B, d = d,
                 k = k, width = var_width)
    })

# Takes simulation results and put them as an exploitable data.frame with only
# gen = 150 abundances
compet_low_cor_var_df = tidy_simulation_list(compet_low_cor_var,
                                             set_of_traits = low_cor_traits,
                                             trait_scenarios = trait_scenarios)

compet_low_cor_var_label = paste0("Competition (A = ", A, "); ",
                                  d * 100, "% dispersal;",
                                  " 3 correlated traits (r = 0.3)")
```

```{r compet_low_cor_df_ind_landscape var_strength}
plot_compet_low_cor_df_ind_var_landscape = fig_ind_landscape(compet_low_cor_var_df,
                                                             compet_low_cor_var_label,
                                                             n_bins = 17)

plot_compet_low_cor_df_ind_var_landscape
```

### High correlations among traits

```{r simul_compet_high_corr var_strength}
compet_high_cor_var <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = uncor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = A, B = B, d = d,
                 k = k, width = var_width)
    })

# Takes simulation results and put them as an exploitable data.frame with only
# gen = 150 abundances
compet_high_cor_var_df = tidy_simulation_list(compet_high_cor_var,
                                              set_of_traits = high_cor_traits,
                                              trait_scenarios = trait_scenarios)

compet_high_cor_var_label = paste0("Competition (A = ", A, "); ",
                                   d * 100, "% dispersal;",
                                   " 3 correlated traits (r = 0.7)")
```

```{r compet_high_cor_df_ind_landscape var_strength}
plot_compet_high_cor_df_ind_var_landscape = fig_ind_landscape(compet_high_cor_var_df,
                                                              compet_high_cor_var_label,
                                                              n_bins = 17)
plot_compet_high_cor_df_ind_var_landscape
```

# Synthetic plots

## R² CWM against environment

```{r synthetic_plot, fig.width=9}
constant_df <- list(no_compet_no_cor_df = no_compet_no_cor_df,
                    no_compet_low_cor_df = no_compet_low_cor_df,
                    no_compet_high_cor_df = no_compet_high_cor_df,
                    compet_no_cor_df = compet_no_cor_df,
                    compet_low_cor_df = compet_low_cor_df,
                    compet_high_cor_df = compet_high_cor_df) %>%
    # Merge as a single data.frame
    bind_rows(.id = "original_name") %>%
    # Extract comptetition and correlation status
    mutate(original_name = gsub("_df", "", original_name)) %>%
    extract(original_name, c("compet_status", "cor_level"),
            "([:alpha:]*_?compet)_(.*)")

var_df <- list(no_compet_no_cor_var_df = no_compet_no_cor_var_df,
               no_compet_low_cor_var_df = no_compet_low_cor_var_df,
               no_compet_high_cor_var_df = no_compet_high_cor_var_df,
               compet_no_cor_var_df = compet_no_cor_var_df,
               compet_low_cor_var_df = compet_low_cor_var_df,
               compet_high_cor_var_df = compet_high_cor_var_df) %>%
    # Merge as a single data.frame
    bind_rows(.id = "original_name") %>%
    # Extract comptetition and correlation status
    mutate(original_name = gsub("_var_df", "", original_name)) %>%
    extract(original_name, c("compet_status", "cor_level"),
            "([:alpha:]*_?compet)_(.*)")

# Combine data.frame from different environment length
all_df <- list(constant = constant_df,
               varying  = var_df) %>%
    bind_rows(.id = "env_width")

# Compute linear models for CWM <-> environment relationship
mod_df <- all_df %>%
    gather("cwm_name", "cwm_value", contains("cwm")) %>%
    group_by(env_width, compet_status, cor_level, scenario, patch, cwm_name) %>%
    summarise(patch_optim = unique(patch_optim), cwm_value = sum(cwm_value)) %>%
    group_by(env_width, compet_status, cor_level, scenario, cwm_name) %>%
    do(mod_cwm_env = lm(cwm_value ~ patch_optim, data = .)) %>%
    ungroup() %>%
    mutate(mod_glance = lapply(mod_cwm_env, broom::glance)) %>%
    unnest(mod_glance)

# R2 plot
plot_r2_cwm_env = ggplot(mod_df %>%
                             filter(!grepl("growth", cwm_name)),
                         aes(scenario, r.squared)) +
    geom_point(aes(fill = fct_rev(cor_level)),
               size = 4, position = position_dodge(width = 0.7),
               shape = 21) +
    facet_grid(rows = vars(compet_status), cols = vars(env_width, cwm_name),
               labeller =
                   labeller(compet_status = c(compet = "Competition",
                                              no_compet = "Only intra comp."),
                            env_width     = c(constant = "Constant\nEnv. Filter Strength",
                                              varying  = "Varying\nEnv. Filter Strength"))) +
    ylim(0, NA) +
    scale_fill_viridis_d("Trait\nCorrelations",
                         labels = c(no_cor   = "r = 0",
                                    low_cor  = "r = 0.3",
                                    high_cor = "r = 0.7")) +
    guides(fill = guide_legend(override.aes = list(size = 4))) +
    labs(subtitle = "R2 of trait2 CWM ~ environment",
         x = "Scenario",
         y = expression("R"^2)) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "top")

plot_r2_cwm_env
```

## Trait variance against environment

```{r plot_trait_var_env}
all_trait_var = all_df %>%
    filter(N > 0) %>%
    group_by(env_width, compet_status, cor_level, scenario, patch) %>%
    summarise_at(vars(matches("trait[123]$")), funs(var = var(.))) %>%
    ungroup() %>%
    mutate(patch_optim = as.numeric(gsub("patches", "", patch))) %>%
    gather("trait_name", "trait_value", contains("trait"))

plot_trait_var_env_constant = ggplot(all_trait_var %>%
                                         filter(env_width == "constant"),
                                     aes(patch_optim, trait_value,
                                         color = trait_name,
                                         linetype = compet_status)) +
    geom_line() +
    facet_grid(vars(cor_level), vars(scenario), scales = "free_y",
               labeller = labeller(scenario = label_value,
                                   cor_level = c(no_cor   = "r = 0",
                                                 low_cor  = "r = 0.3",
                                                 high_cor = "r = 0.7"))) +
    scale_color_discrete(name = "Trait",
                         labels = c(trait1_var = "Trait 1",
                                    trait2_var = "Trait 2",
                                    trait3_var = "Trait 3")) +
    scale_linetype_discrete(name = NULL,
                            labels = c(compet    = "Competition",
                                       no_compet = "Only intra comp.")) +
    labs(x = "Environment",
         y = "Trait Variance",
         subtitle = "Constant Environment") +
    theme(legend.position = "top")

plot_trait_var_env_constant

cat('\r\n\r\n')

plot_trait_var_env_varying = ggplot(all_trait_var %>%
                                        filter(env_width == "varying"),
                                    aes(patch_optim, trait_value,
                                        color = trait_name,
                                        linetype = compet_status)) +
    geom_line() +
    facet_grid(vars(cor_level), vars(scenario), scales = "free_y",
               labeller = labeller(scenario = label_value,
                                   cor_level = c(no_cor   = "r = 0",
                                                 low_cor  = "r = 0.3",
                                                 high_cor = "r = 0.7"))) +
    scale_color_discrete(name = "Trait",
                         labels = c(trait1_var = "Trait 1",
                                    trait2_var = "Trait 2",
                                    trait3_var = "Trait 3")) +
    scale_linetype_discrete(name = NULL,
                            labels = c(compet    = "Competition",
                                       no_compet = "Only intra comp.")) +
    labs(x = "Environment",
         y = "Trait Variance",
         subtitle = "Varying Environment") +
    theme(legend.position = "top")

plot_trait_var_env_varying

cat('\r\n\r\n')

```

```{r link_r2_cwm_trait_var}

mod_df$contrib2 <- as.numeric(gsub(".*R|A.*", "",
                                   mod_df$scenario))
mod_df$contrib1 <- 100 - mod_df$contrib2

all_trait_var$contrib2 <- as.numeric(gsub(".*R|A.*", "",
                                          all_trait_var$scenario))
all_trait_var$contrib1 <- 100 - all_trait_var$contrib2

# Plot
plot_grid(
    ggplot(mod_df[which(mod_df$env_width == "constant" &
                            mod_df$compet_status == "compet" &
                            mod_df$cwm_name == "trait2_cwm"), ],
           aes(as.factor(contrib2), adj.r.squared)) +
        geom_boxplot(aes(fill = cor_level)) +
        scale_fill_viridis_d("Trait\nCorrelations",
                             labels = c(no_cor   = "r = 0",
                                        low_cor  = "r = 0.3",
                                        high_cor = "r = 0.7")) +
        labs(x = "Contribution of trait2 to growth (in %)",
             y = "R² of the relationship between\nCWM and environment"),
    ggplot(all_trait_var[which(all_trait_var$compet_status == "compet" &
                                   all_trait_var$env_width == "constant" &
                                   all_trait_var$trait_name == "trait2_var"), ],
           aes(as.factor(contrib2), trait_value)) +
        geom_boxplot(aes(fill = cor_level)) +
        scale_fill_viridis_d("Trait\nCorrelations",
                             labels = c(no_cor   = "r = 0",
                                        low_cor  = "r = 0.3",
                                        high_cor = "r = 0.7")) +
        labs(x = "Contribution of trait2 to growth (in %)",
             y = "Variance of trait2 within the patch"),
    nrow = 2)

ggplot(all_trait_var, aes(scenario, trait_value, fill = fct_rev(cor_level))) +
    geom_boxplot() +
    facet_grid(rows = vars(env_width, compet_status),
               cols = vars(trait_name),
               labeller =
                   labeller(compet_status = c(compet = "Competition",
                                              no_compet = "Only intra comp."),
                            env_width     = c(constant = "Constant\nEnv. Filter Strength",
                                              varying  = "Varying\nEnv. Filter Strength")),
               scales = "free_y") +
        scale_fill_viridis_d("Trait\nCorrelations",
                             labels = c(no_cor   = "r = 0",
                                        low_cor  = "r = 0.3",
                                        high_cor = "r = 0.7")) +
        labs(y = "Variance of trait across all patches")

cat('\r\n\r\n')

```

## CWV against environment

```{r cwv_envt}

var_df %>%
    select(-contains("cwm")) %>%
    filter(compet_status == "no_compet") %>%
    gather("trait_name", "trait_value", contains("trait")) %>%
    group_by(compet_status, cor_level, scenario, patch, trait_name) %>%
    summarise(trait_cwv = Weighted.Desc.Stat::w.var(trait_value, mu = N)) %>%
    mutate(patch_optim = gsub("patches", "", patch) %>%
               as.numeric()) %>%
    ggplot(aes(patch_optim, trait_cwv, color = trait_name)) +
    geom_point() +
    geom_smooth(se = FALSE) +
    facet_grid(vars(cor_level), vars(scenario), scales = "free_y",
               labeller = labeller(scenario = label_value,
                                   cor_level = c(no_cor   = "r = 0",
                                                 low_cor  = "r = 0.3",
                                                 high_cor = "r = 0.7"))) +
    scale_color_discrete(labels = c(trait1_cwm = "Trait 1",
                                    trait2_cwm = "Trait 2",
                                    trait3_cwm = "Trait 3")) +
    labs(x = "Environment",
         y = "Community-Weighted Variance (CWV)",
         color = NULL,
         subtitle = paste0("Varying environment; ",
                           d * 100, "% dispersal;",
                           " Only intra comp.")) +
    theme(legend.position = "top")

cat('\r\n\r\n')

var_df %>%
    select(-contains("cwm")) %>%
    filter(compet_status == "compet") %>%
    gather("trait_name", "trait_value", contains("trait")) %>%
    group_by(compet_status, cor_level, scenario, patch, trait_name) %>%
    summarise(trait_cwv = Weighted.Desc.Stat::w.var(trait_value, mu = N)) %>%
    mutate(patch_optim = gsub("patches", "", patch) %>%
               as.numeric()) %>%
    ggplot(aes(patch_optim, trait_cwv, color = trait_name)) +
    geom_point() +
    geom_smooth(se = FALSE) +
    facet_grid(vars(cor_level), vars(scenario), scales = "free_y",
               labeller = labeller(scenario = label_value,
                                   cor_level = c(no_cor   = "r = 0",
                                                 low_cor  = "r = 0.3",
                                                 high_cor = "r = 0.7"))) +
    scale_color_discrete(labels = c(trait1_cwm = "Trait 1",
                                    trait2_cwm = "Trait 2",
                                    trait3_cwm = "Trait 3")) +
    labs(x = "Environment",
         y = "Community-Weighted Variance (CWV)",
         color = NULL,
         subtitle = paste0("Varying environment; ",
                           d * 100, "% dispersal;",
                           " Competition")) +
    theme(legend.position = "top")

```

>>>>

# Define meta-function to run all analyses with many trait levels --------------

meta_simul = function(seed_number) {
    set.seed(seed_number)
    uncor_traits = generate_cor_traits(n_patches, n_species, n_traits - 1,
                                       cor_coef = 0)
    set.seed(seed_number)
    low_cor_traits = generate_cor_traits(n_patches, n_species, n_traits - 1,
                                         cor_coef = 0.3)

    set.seed(seed_number)
    high_cor_traits = generate_cor_traits(n_patches, n_species, n_traits - 1,
                                          cor_coef = 0.7)
    all_cor = list(uncor    = uncor_traits,
                   low_cor  = low_cor_traits,
                   high_cor = high_cor_traits)

    all_env = list(constant = env_width,
                   varying  = var_width)

    all_compet = list(no_compet = list(A = 0, B = B),
                      compet    = list(A = A, B = B))

    all_facets = expand.grid(compet_status = names(all_compet),
                             env_width     = names(all_env),
                             cor_level     = names(all_cor),
                             scenario      = names(trait_scenarios))

    apply(all_facets, 1, function(given_row) {
        multigen(traits = all_cor[[given_row[["cor_level"]]]],
                 trait_weights = trait_scenarios[[given_row[["scenario"]]]],
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = all_compet[[given_row[["compet_status"]]]][["A"]],
                 B = all_compet[[given_row[["compet_status"]]]][["B"]],
                 d = d,
                 k = k,
                 width = all_env[[given_row[["env_width"]]]]) %>%
            landscape_df(all_cor[[given_row[["cor_level"]]]],
                         trait_scenarios[[given_row[["scenario"]]]],
                         time = 150) %>%
            inner_join(all_cor[[given_row[["cor_level"]]]] %>%
                           as.data.frame() %>%
                           rownames_to_column("species"),
                       by = "species") %>%
            group_by(patch) %>%
            mutate(rel_abund = N/sum(N)) %>%
            ungroup() %>%
            mutate(compet_status = given_row[["compet_status"]],
                   env_width     = given_row[["env_width"]],
                   cor_level     = given_row[["cor_level"]],
                   scenario      = given_row[["scenario"]],
                   seed_number = seed_number) %>%
            select(seed_number, compet_status, env_width, cor_level, scenario,
                   everything())
    }) %>%
        bind_rows() %>%
        filter(N != 0) %>%  # Take out absent species
        mutate_at(vars(contains("trait")), funs(cwm = rel_abund * .)) %>%
        mutate(scenario = fct_relevel(scenario, names(trait_scenarios)),
               patch_optim = as.numeric(gsub("patches", "", patch))) %>%
        group_by(seed_number, compet_status, env_width, cor_level, scenario,
                 patch) %>%
        summarise(trait1_cwm  = sum(trait1_cwm),
                  trait2_cwm  = sum(trait2_cwm),
                  trait3_cwm  = sum(trait3_cwm),
                  trait1_var  = var(trait1),
                  trait2_var  = var(trait2),
                  trait3_var  = var(trait3),
                  patch_optim = unique(patch_optim))
}

@@

```{r}
library("furrr")

plan(multiprocess)
tictoc::tic()

first_simuls = future_map(1:60, function(x) {
    devtools::load_all()

    meta_simul(x) %>%
        gather("cwm_name", "cwm_value", ends_with("cwm")) %>%
        group_by(cwm_name, add = TRUE) %>%
        do(mod_cwm_env = lm(cwm_value ~ patch_optim, data = .)) %>%
        ungroup() %>%
        mutate(mod_glance = lapply(mod_cwm_env, broom::glance)) %>%
        unnest(mod_glance)
}) %>%
    bind_rows()

tictoc::toc()
```
